---
title: "Test2"
output: html_document
---


Load and rename the Abalone data
```{r}
# Retreive the abalone dataset from online, as we did in class
uciaddress <- "http://archive.ics.uci.edu/ml/machine-learning-databases/" 
dataset <- "abalone/abalone.data"
getdataset <- paste(uciaddress, dataset, sep="")
abalone <- read.csv(getdataset)

#rename the column names of abalone dataset
colnames(abalone) <- c("Gender","Length","Diameter",
                       "Height", "Whole_wgt",
                       "Shucked_wgt", "Viscera wgt",
                       "Shell wgt", "Rings")

```

1. Get a dataset of the sample sizes of 1%, 10%, 25%, 50%, 80%, and 100%
```{r}

SampleSummary = function(dataframe,column,n){    #Create the function SampleSummary that takes a dataframe and column name
  new<-as.integer(nrow(dataframe)*n) #create the variable new as the the integer the percent of the dataframe
  number<-grep(column, colnames(dataframe)) #aasign to the new varaible number the index of the column
  dat<-dataframe[sample(nrow(dataframe), new),number] #create variable dat 
  min<-min(dat) #get the min of the sample
  max<-max(dat)#get the max of the sample
  mean<-mean(dat)#get the mean of the sample
  var<-var(dat)#get the variance of the sample
  new.data<-data.frame(min, max, mean, var) #create new dataframe
  return(new.data)
} #return the new dataframe with 1 column and 4 variables


#function to get the dataframe samples, which has defined rows and columns and contains the min, max, mean and var (as rows) for each of the sample sizes(as columns)

datasamples<-function(dataframe, column){
  j<-1
  df<-data.frame(matrix(NA, nrow=4,ncol=6))
  for(n in c(.01, .10, .25, .5, .8, 1)){
  first<-SampleSummary(dataframe,column, n)
  df[j]<-as.numeric(first)
  j<-j+1
  }
rownames(df)<-c("SampleMin", "SampleMax", "SampleMean", "SampleVar")
colnames(df)<-c(".01", ".10", ".25", ".50", ".80", "1.00")
return(df)
}
samples<-datasamples(abalone, 'Whole_wgt') 
str(samples)
```


2. Create a grid of histograms with all sample sizes
```{r}
#function plots that takes in a dataframe and returns a grid of histograms, colored per varaible
plots<-function(dataframe){
  require(ggplot2)
  require(grid)
  require(gridExtra)
  j<-0
  i<-0
  plots<-c()
  for(i in 1:6){
    j<-j+1
    name<-ggplot(dataframe, aes(x=dataframe[[i]], fill=factor(rownames(dataframe))), environment=environment())
    name<-name+geom_histogram(binwidth=.05)+
      labs(x="Color") + labs(title=paste(colnames(dataframe)[j], "SampleHist" , sep="_"))+ theme(legend.title=element_blank())
    plotname<-paste(colnames(samples)[j], 'Sample', sep='_')
    plots[[plotname]]<-name
  }
histos<-do.call(grid.arrange, plots)
return(histos)
}
plots(dataframe=samples)


```


3. Loop of 1,000
```{r}
#function loop that takes a dataframe and column as inputs and returns 
loop<-function(dataframe, column){
  mean.data<-data.frame("1%"=rep(0,1000), "10%"=rep(0,1000), "25%"=rep(0,1000), "50%"=rep(0,1000), "80%"=rep(0,1000))
k<-0
  for(i in c(.01, .1, .25, .5, .8)){ #here is where it makes it much easier to just have the 100% sample too
    row<-rep(0,1000)
    for(j in 1:1000){
      new<-SampleSummary(dataframe, column, i)$mean
      row[j]<-new
      
    }
    k<-k+1
    mean.data[k]<-row
  }
  colnames(mean.data)<-c(".01", ".10", ".25", ".50", ".80")
  str(mean.data)
  return(mean.data)
}
mean.data<-loop(abalone, 'Whole_wgt')


```

4. Histogram of means from the samples above and the 100% sample
```{r}

#this takes a reeeaaaaalllllly long time
addhundop<-function(df1, df2, column){
  number<-grep(column, colnames(df2))
  hundred<-rep(mean(df2[,number]), 1000)
  df1["1.00"]<-hundred
  return(df1)
}
mean.data<-addhundop(mean.data, abalone, 'Whole_wgt')


plots(mean.data) #i'm not sure this is entirely correct...... there is only one variable for each sample, true, but what is with the changing colors then? is it really only supposed to be one bar?
str(mean.data)

```

5. Min, Max, Mean and Var for dataframe from #3 (mean.data) 
```{r}

#NOT SURE IF I NEED TO APPEND ROWS OR COLUMNS.....
combine<-function(data){
  mean.summary<-data.frame(matrix(NA, nrow=4, ncol=6))
  j<-1
  for(i in colnames(mean.data)){
    first<-SampleSummary(mean.data, i, 1) #n=1 because we want the whole of each column
    mean.summary[j]<-as.numeric(first)
    j<-j+1
  }
  colnames(mean.summary)<-c(".01", ".10", ".25", ".50", ".80", "1.00")
  rownames(mean.summary)<-c("ReSampleMin", "ReSampleMax", "ReSampleMean", "ReSampleVar")
  new.data<-rbind(samples, mean.summary)
  return(new.data)
}
new.data<-combine(mean.data)
str(new.data)
rownames(new.data)

```

6. Histogram of 100% data with SampleMean data overlayed
```{r}

#STILL NEED TO LABEL EACH VERITCAL LINE, AND COLOR CODE INDIVIDUAL VARIABLES

#plot the 100% data
name2<-function(column){
  n2<-NULL
  n2<-ggplot(new.data, aes(x=new.data[[6]], fill=factor(rownames(new.data))),     environment=environment())
  n2<-n2+geom_histogram(binwidth=.05)+
    labs(x="Color") + labs(title="100% Sample Histogram")
for(i in seq(2:ncol(new.data))){ 
    n2<-n2+geom_vline(xintercept=new.data[column, i], colour='black') + annotate("text",x=new.data[column, i],y=i/5, label=colnames(new.data)[i], hjust=0) + theme(legend.title=element_blank())
}
  return(n2)
}
name2("SampleMean")


```


7. Histogram of 100% data with ReSampleMean data overlayed
```{r}
name2("ReSampleMean")

```


8. Apply to diamonds$carat and faithful$eruptions
```{r}
datas<-c(abalone, diamonds, faithful)
columns<-c('Whole_wgt', 'carat', 'eruptions')
j<-0
for(i in datas){
  j<-j+1
  dataframe<-i
  column<-columns[j]
dataframe<-faithful
column<-'eruptions'
  samples<-datasamples(dataframe, column)
  plots(samples)
  mean.data<-loop(dataframe, column)
  mean.data<-addhundop(mean.data, dataframe, column)
  plots(mean.data)
  new.data<-combine(mean.data)
  name2("SampleMean")
  name2("ReSampleMean")
}
str(mean.data)
columns[1]
```

9. Taking many samples and taking the mean gets you a better estimate than taking just one random sample and taking the mean. When you put these means in a dataframe, you realize that they are all much closer to the actual mean than a one sample mean


