---
title: "Test2"
output: html_document
---


Load and rename the Abalone data
```{r}
####THIS IS TAKEN FROM R_DATA_ANALYSIS.RMD
# UCI is a great resource for datasets. Here's an example of how to 
# retrieve the Abalone data
uciaddress <- "http://archive.ics.uci.edu/ml/machine-learning-databases/"
dataset <- "abalone/abalone.data"
getdataset <- paste(uciaddress, dataset, sep="")
abalone <- read.csv(getdataset)
colnames(abalone) <- c("Gender","Length","Diameter",
                       "Height", "Whole_wgt",
                       "Shucked_wgt", "Viscera wgt",
                       "Shell wgt", "Rings")

```

1. Get a dataset of the sample sizes of 1%, 10%, 25%, 50%, 80%, and 100%
```{r}

SampleSummary = function(dataframe,column,n){    #Create the function SampleSummary that takes a dataframe, column name, sample size and 
  new<-as.integer(nrow(dataframe)*n) #create the variable new as the the integer the percent of the dataframe
  number<-grep(column, colnames(dataframe)) #aasign to the new varaible number the index of the column
  dat<-dataframe[sample(nrow(dataframe), new),number]
  min<-min(dat) #get the min of the sample
  max<-max(dat)#get the max of the sample
  mean<-mean(dat)#get the mean of the sample
  var<-var(dat)#get the variance of the sample
  new.data<-data.frame(min, max, mean, var) #create new dataframe
  return(new.data)
} #return the new dataframe with 1 column and 4 variables


#function to get the dataframe samples, which has defined rows and columns and contains the min, max, mean and var (as rows) for each of the sample sizes(as columns)

datasamples<-function(dataframe, column){
  j<-1
  df<-data.frame(matrix(NA, nrow=4,ncol=6))
  for(n in c(.01, .10, .25, .5, .8, 1)){
  first<-SampleSummary(dataframe,column, n)
  df[j]<-as.numeric(first)
  j<-j+1
  }
rownames(df)<-c("SampleMin", "SampleMax", "SampleMean", "SampleVar")
colnames(df)<-c(".01", ".10", ".25", ".50", ".80", "1.00")
return(df)
}
samples<-datasamples(abalone, 'Whole_wgt') 
str(samples)
```


2. Create a grid of histograms with all sample sizes
```{r}
#function plots that takes in a dataframe and returns a grid of histograms, colored per varaible
library(ggplot2)
require(grid)
require(gridExtra)
plots<-function(dataframe){
  j<-0
  i<-0
  plots<-c()
  for(i in 1:6){
    j<-j+1
    name<-ggplot(dataframe, aes(x=dataframe[[i]], fill=factor(rownames(dataframe))), environment=environment())
    name<-name+geom_histogram(binwidth=.05)+
      labs(x="Color") + labs(title=paste(colnames(dataframe)[j], "SampleHist" , sep="_"))+ theme(legend.title=element_blank())
    plotname<-paste(colnames(samples)[j], 'Sample', sep='_')
    plots[[plotname]]<-name
  }
histos<-do.call(grid.arrange, plots)
return(histos)
}
plots(dataframe=samples)


```


3. Loop of 1,000
```{r}
loop<-function(dataframe, column){
  mean.data<-data.frame("1%"=rep(0,1000), "10%"=rep(0,1000), "25%"=rep(0,1000), "50%"=rep(0,1000), "80%"=rep(0,1000))
k<-0
  for(i in c(.01, .1, .25, .5, .8)){ #here is where it makes it much easier to just have the 100% sample too
    row<-rep(0,1000)
    for(j in 1:1000){
      new<-SampleSummary(dataframe, column, i)$mean
      row[j]<-new
      
    }
    k<-k+1
    mean.data[k]<-row
  }
  colnames(mean.data)<-c(".01", ".10", ".25", ".50", ".80")
  str(mean.data)
  return(mean.data)
}
mean.data<-loop(abalone, 'Whole_wgt')


```

4. Histogram of means from the samples above and the 100% sample
```{r}

#this takes a reeeaaaaalllllly long time
addhundop<-function(df1, df2, column){
  number<-grep(column, colnames(df2))
  hundred<-rep(mean(df2[,number]), 1000)
  df1["1.00"]<-hundred
  return(df1)
}
mean.data<-addhundop(mean.data, abalone, 'Whole_wgt')


plots(mean.data) #i'm not sure this is entirely correct...... there is only one variable for each sample, true, but what is with the changing colors then? is it really only supposed to be one bar?

```

5. Min, Max, Mean and Var for dataframe from #3 (mean.data) 
```{r}

#NOT SURE IF I NEED TO APPEND ROWS OR COLUMNS.....
combine<-function(data){
  mean.summary<-data.frame(matrix(NA, nrow=4, ncol=6))
  j<-1
  for(i in colnames(mean.data)){
    first<-SampleSummary(mean.data, i, 1) #n=1 because we want the whole of each column
    mean.summary[j]<-as.numeric(first)
    j<-j+1
  }
  colnames(mean.summary)<-c(".01", ".10", ".25", ".50", ".80", "1.00")
  rownames(mean.summary)<-c("ReSampleMin", "ReSampleMax", "ReSampleMean", "ReSampleVar")
  new.data<-rbind(samples, mean.summary)
  return(new.data)
}
new.data<-combine(mean.data)
str(new.data)
rownames(new.data)

```

6. Histogram of 100% data with SampleMean data overlayed
```{r}
library(quadprog)
library(directlabels)
library(grid)
#STILL NEED TO LABEL EACH VERITCAL LINE, AND COLOR CODE INDIVIDUAL VARIABLES

#plot the 100% data
name2<-function(column){
  name2<-NULL
  name2<-ggplot(new.data, aes(x=new.data[[6]], fill=factor(rownames(new.data))),     environment=environment())
  name2<-name2+geom_histogram(binwidth=.05)+
    labs(x="Color") + labs(title="100% Sample Histogram")
for(i in seq(2:ncol(new.data))){ 
    name2<-name2+geom_vline(xintercept=new.data[column, i], colour='black') + annotate("text",x=new.data[column, i],y=i, label=colnames(new.data)[i], hjust=0) + theme(legend.title=element_blank())
}
  return(name2)
}
name2("SampleMean")
direct.label(name)
name2("SampleMean")
new.data["SampleMean",1]
resample<-str(colnames(new.data["ReSampleMean",]))
resample
samp<-new.data["SampleMean", ]
```


7. Histogram of 100% data with ReSampleMean data overlayed
```{r}
name2("ReSampleMean")

```


8. Apply to diamonds$carat and faithful$eruptions
```{r}
datas<-c(abalone, diamonds, faithful)
columns<-c('Whole_wgt', 'carat', 'eruptions')
for(i in datas){
  j<-j+1
  dataframe<-i
  column<-columns[j]
  samples<-datasamples(dataframe, column)
  plots(samples)
  mean.data<-loop(dataframe, column)
  mean.data<-addhundop(mean.data, dataframe, column)
  plots(mean.data)
  new.data<-combine(mean.data)
  graphsample<-name2("SampleMean")
  graphresample<-name2("ReSampleMean")
}

```

9. Taking many samples and taking the mean gets you a better estimate than taking just one random sample and taking the mean. When you put these means in a dataframe, you realize that they are all much closer to the actual mean than a one sample mean



1. Should be 6 columns, not 5. Create functions for mean, max, etc. RANDOM SAMPLES-set a seed-->what is that? is that included in the code above?
2. Create function for histogram
3. new dataframe has 5 columns, with 1000 rows. Each row is the mean you calculate from the % sample.
4. Reuse function from #2
5. 
6. vertical line
7. 
8. 
9. 
